The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-20 analysis/paper/paper.qmd
Add locaiton as argument to geocode function

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                         # Managing paths
  "tidyverse",                    # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm",  # Text processing and analysis
  "tidygeocoder",                 # Working with spatial data
  "igraph", "ggraph"              # Network analysis and visualsation
)

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
  library(package, character.only = TRUE)
}

@@

# Read thesis metadata ----
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

## Read metadata for all theses
all_theses <-
  readxl::read_xlsx(path = here(data_path, "theses-all.xlsx"))

## Read only metadata for theses with PDF available
emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) %>%
  mutate(text = "") %>%
  filter(!is.na(pdf_via))

@@

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up

emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(all_theses)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(all_theses$grad_year, na.rm = TRUE), "-", max(all_theses$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.

@@

# Geocode thesis locations
emu_theses <- emu_theses %>%
  geocode(location, method = 'osm', lat = latitude , long = longitude)

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_point(data = emu_theses, aes(longitude, latitude), color = "red") +
  coord_fixed() +
  theme_void()
```

>>>>

# Load packages ----
## Managing paths
library(here)

## Data manipulation and visualisation
library(tidyverse)

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)

## Working with spatial data
library(tidygeocoder)

@@

# Read thesis metadata ----
## All theses
theses_all <-
  readxl::read_xlsx(path = here("analysis", "data", "raw_data", "theses-all.xlsx"))

## Theses with PDF available
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) %>%
  mutate(text = "") %>%
  filter(!is.na(pdf_via))

@@

```{r}
#| label: extract-pdf-text
#| echo: false
emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(theses_all)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(theses_all$grad_year, na.rm = TRUE), "-", max(theses_all$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.

@@

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, "location")

# Show thesis locations on world map
visualize_thesis_locations(emu_theses)
```
